My title

### 2024-03-06 paper/paper.qmd
The pdf now renders the working model

library(tidyverse)
library(palmerpenguins)
library(boot)
library(broom.mixed)
library(collapse)
library(gutenbergr)
library(janitor)
library(knitr)
library(marginaleffects)
library(modelsummary)
library(rstanarm)
library(tidybayes)
```

@@

\begin{align} 
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{gender}_i + \beat_2 \times \mbox{education}_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\beta_2 &\sim \mbox{Normal}(0, 2.5)
\end{align}

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

>>>>

library(tidyverse)
library(palmerpenguins)
library(boot)
library(broom.mixed)
library(collapse)
library(gutenbergr)
library(janitor)
library(knitr)
library(marginaleffects)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(arrow)
library(dplyr)
```

@@

\begin{align} 
y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \\
\mbox{logit}(\pi_i) &= \alpha + \beta_1 \times \mbox{gender}_i + \beta_2 \times \mbox{education}_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 5.02) \\
\beta_2 &\sim \mbox{Normal}(0, 6.34)
\end{align}

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))

ces2020_reduced <- 
  analysis_data |> 
  slice_sample(n = 1000)
